Type-Safe Modular Parsing

### 2017-06-14 SLE_17/sections/CaseStudy.tex
Spellcheck

The right part of table \ref{tab:comparison} suggests that the difference of running time between
using Object Algebras and class is little, roughly 1\%.
The usage of longest match combinator slows the performance by 7\%. The main reason of slower
execution time may be the overall structure of the modular parsing approach, because we indeed have
more intermediate function calls and method overriding. However, it is worth mentioning that
because of the memoization technique of Packrat parsers, we are only constant times
slower, the algorithmic complexity is still the same.
Since the slowdown seems to be caused by extra method
dispatching, in future work we wish to investigate techniques such as 
partial evaluation or meta-programming to eliminate such cost. The
work by B{\'e}guet and Manohar~\cite{Beguet:2014} is an interesting starting point.

>>>>

The right part of table \ref{tab:comparison} suggests that the difference of running time between
using Object Algebras and class is little, roughly 1\%.
The usage of longest match combinator slows the performance by 7\%. The main reason of slower
execution time may be the overall structure of the modular parsing approach, because we indeed have
more intermediate function calls and method overriding. However, it is worth mentioning that
because of the memorization technique of Packrat parsers, we are only constant times
slower, the algorithmic complexity is still the same.
Since the slowdown seems to be caused by extra method
dispatching, in future work we wish to investigate techniques such as
partial evaluation or meta-programming to eliminate such cost. The
work by B{\'e}guet and Manohar~\cite{Beguet:2014} is an interesting starting point.

### 2017-06-14 SLE_17/sections/Introduction.tex
Revision
Spellcheck

\item \textbf{TAPL case study:} We conduct a case study with 18 interpreters
  from the TAPL book. The case study show the effectiveness of modular
  parsing in terms of reuse. The TAPL case study is available online
  at:
  \url{https://github.com/lihuanglx/modular-parsing}

@@

All the code in the paper and the case study is written in Scala, since its concise and elegant
syntax gives better presentation. Other languages that support some form of multiple inheritance
(including C++ or Java 8 with default methods~\cite{Goetz2012}) could in principle be
used.

>>>>

\item \textbf{TAPL case study:} We conduct a case study with 18 interpreters
  from the TAPL book. The case study shows the effectiveness of modular
  parsing in terms of reuse. The TAPL case study is available online
  at:

  \url{https://github.com/lihuanglx/modular-parsing}

@@

All the code in the paper and the case study is written in Scala, since its concise and elegant
syntax is good for presentation. Other languages that support some form of multiple inheritance
(including C++ or Java 8 with default methods~\cite{Goetz2012}) could in principle be
used.

### 2017-06-14 SLE_17/sections/PackratParsing.tex
Spellcheck

Similarly, this violates a modular setting because it also requires a global view of the full grammar.
Hence the worst case where all alternatives may share common prefixes with future cases
should always be antecipated. Therefore we need to backtrack for all the branches. To avoid failures in the future, we have to add \inlinecode{try} everywhere. However this results in the worst-case exponential time
complexity.

\subsection{Packrat Parsing}\label{subsec:packratparsing}
Fortunately, some more advanced parsing techniques such as Packrat
parsing~\cite{Ford2002} have been developed to address limitations of
simple parser combinators. Packrat parsing uses memoization to record
the result of applying each parser at each position of the input, so
that repeated computation is eliminated. Moreover, it supports both direct left-recursion
and (in theory) indirect left-recursion~\cite{warth2008}.
All of these properties are very suitable for modularity, thus we decided to use Packrat parsers as the underlying parsing technique for modular parsing.
\begin{comment}
It is worth mentioning that the choice of parser combinators will not
affect the other parts of our library. One can choose other parser
combinators like Parsec, in cases that the performance and supporting
of left-recursion are not major concerns. A different library can even build a new
\name with fancy features or higher efficiency.
\end{comment}
Scala has a standard parser combinator library\footnote{https://github.com/scala/scala-parser-combinators}
\cite{moors2008parser} for Packrat parsers.
The library provides a number of parser combinators, including the longest match alternative combinator.
%Below we present an example to illustrate Scala parsers.

@@

It is worth mentioning that the left-recursive grammar above is well supported without extra code.
 The longest match composition is also employed by using the combinator \lstinline{|||}. Furthermore, the parser does not suffer from the backtracking problem, as the memoization technique of Packrat parsing guarantees reasonable efficiency.

>>>>

Similarly, this violates a modular setting because it also requires a global view of the full grammar.
Hence the worst case where all alternatives may share common prefixes with future cases
should always be anticipated. Therefore we need to backtrack for all the branches. To avoid failures in the future, we have to add \inlinecode{try} everywhere. However this results in the worst-case exponential time
complexity.

\subsection{Packrat Parsing}\label{subsec:packratparsing}
Fortunately, some more advanced parsing techniques such as Packrat
parsing~\cite{Ford2002} have been developed to address limitations of
simple parser combinators. Packrat parsing uses memorization to record
the result of applying each parser at each position of the input, so
that repeated computation is eliminated. Moreover, it supports both direct left-recursion
and (in theory) indirect left-recursion~\cite{warth2008}.
All of these properties are very suitable for modularity, thus we decided to use Packrat parsers as the underlying parsing technique for modular parsing.
\begin{comment}
It is worth mentioning that the choice of parser combinators will not
affect the other parts of our library. One can choose other parser
combinators like Parsec, in cases that the performance and supporting
of left-recursion are not major concerns. A different library can even build a new
\name with fancy features or higher efficiency.
\end{comment}
Scala has a standard parser combinator library\footnote{https://github.com/scala/scala-parser-combinators}
\cite{moors2008parser} for Packrat parsers.
The library provides a number of parser combinators, including the longest match alternative combinator.
%Below we present an example to illustrate Scala parsers.

@@

It is worth mentioning that the left-recursive grammar above is well supported without extra code.
 The longest match composition is also employed by using the combinator \lstinline{|||}. Furthermore, the parser does not suffer from the backtracking problem, as the memorization technique of Packrat parsing guarantees reasonable efficiency.
